---
title: "PS811 Portfolio"
author: "Juan Qian"
output:
  html_document: 
    toc: true ## table of contents
    code_folding: hide
---
```{r setup, include=FALSE}
## Defaults for R chunks
knitr::opts_chunk$set(echo = TRUE, ## echo = TRUE means code will show
                      warning=FALSE, ## supress warnings and messages from R
                      message=FALSE,
                      fig.path='Figs/', ## where to save figures
                      fig.height = 3, ## default figure size (can differ in each chunk)
                      fig.width = 3)

## Add any R packages you require. 
## Here are some we will use in 811:
requires <- c("tidyverse", ## tidyverse includes dplyr and ggplot2
              "magrittr",
              "foreign",
              "readstata13",
              "here")

## Install any you don't have
to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )

## Load all required R packages
library(tidyverse)
library(ggplot2); theme_set(theme_minimal())
library(magrittr)
library(here)
```
<!-- The above header sets everything up. -->





<!-- Replace the below with bit about you. -->
### Personal Background
I am a doctoral student in the Political Science Department at the University of Wisconsin-Madison. My fields of interest are political methodology and comparative politics.

Prior to graduate school, I served as an Associate in Research at the Margolis Center for Health Policy at Duke University from 2016-18. Additionally, I worked for several government agencies and and think tanks, including Minnesota Senate, Office of Minnesota Governor, and American Enterprise Institute.

My hometown is Nanjing, a city in eastern China. I graduated from Macalester College with a B.A. in political science in 2014 and obtained his Master of Public Policy from Georgetown University in 2016.

### Research Interests
I am interested in how the Chinese citizens' attitudes toward government vary by province and a respondent's personal characteristics. 

### Motivation & Background
The core question is: In a specific province, does gender affect one's perception of local government performance?
## Why Gender Matters?
Many studies find that males and females have different views on certain political issues. Under authoritarian regimes specifically,

### Relevant Data
China Family Panel Studies (https://www.icpsr.umich.edu/icpsrweb/ICPSR/studies/36524)'s 2014 data

China Multi-Generational Panel Dataset, Liaoning (CMGPD-LN), 1749-1909 (https://www.icpsr.umich.edu/icpsrweb/ICPSR/studies/27063)

### Data Visualization
To answer this question, I calculated and created a plot that shows the citizens' average attitudes toward government in each province, breaking up by gender.


```{r ggplot, fig.height = 6, fig.width = 6}
dat <- read.csv("data/CFPS.csv")
## Read data from China Family Panel Studies into the dataset
dat$maleapproval <- 5-dat$male_approval ## Rescaled my government approaval scale from 1(best), 5(worst) to 1(worst), 5(best)
dat$femaleapproval <- 5-dat$female_approval 
ggplot() +
  # define y = province level for all layers
  aes(y = dat$province) +
  # x = points for each actor
  geom_point(aes(x = dat$maleapproval), shape = "M", color= "blue", size=3) + 
  geom_point(aes(x = dat$femaleapproval), shape = "F", color= "red", size=3) +
  ggtitle("PRC Citizen's Attitudes toward Government, by Province") +
  geom_segment(aes(x = dat$maleapproval, 
                   xend = dat$femaleapproval, 
                   yend = dat$province), 
               color = dat$regioncolor, 
               size = 3, 
               lineend = "round", 
               alpha = .3) +
  labs(y = "Province", 
       x = "Local Government Approval (worst=1, best=5)", size=3)
```

