---
title: "PS811 Portfolio"
author: "Juan Qian"
output:
  html_document: 
    toc: true ## table of contents
    code_folding: hide
---
```{r setup, include=FALSE}
## Defaults for R chunks
knitr::opts_chunk$set(echo = TRUE, ## echo = TRUE means code will show
                      warning=FALSE, ## supress warnings and messages from R
                      message=FALSE,
                      fig.path='Figs/', ## where to save figures
                      fig.height = 3, ## default figure size (can differ in each chunk)
                      fig.width = 3)

## Add any R packages you require. 
## Here are some we will use in 811:
requires <- c("tidyverse", ## tidyverse includes dplyr and ggplot2
              "magrittr",
              "foreign",
              "readstata13",
              "here")

## Install any you don't have
to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )

## Load all required R packages
library(tidyverse)
library(ggplot2); theme_set(theme_minimal())
library(magrittr)
library(here)
```
<!-- The above header sets everything up. -->





<!-- Replace the below with bit about you. -->
### Personal Background
I am a doctoral student in the Political Science Department at the University of Wisconsin-Madison. My fields of interest are political methodology and comparative politics.

Prior to graduate school, I served as an Associate in Research at the Margolis Center for Health Policy at Duke University from 2016-18. Additionally, I worked for several government agencies and and think tanks, including Minnesota Senate, Office of Minnesota Governor, and American Enterprise Institute.

My hometown is Nanjing, a city in eastern China. I graduated from Macalester College with a B.A. in political science in 2014 and obtained his Master of Public Policy from Georgetown University in 2016.

### Research Interests
I am interested identities and narratives of social groups, and how the people's identities influenced their political behavior and interaction with political institutions. Specifically, I am interested in exploring the reason why some ethnic minority groups in China assimilate with the mainstream society, while other groups chose to resist the forced assimilation by authoritarian institutions.

Methodologically, I am interested in developing automated text analysis (reuse, topic models and other Bayesian classifiers, content analysis) to assist my research in group identities and narratives.

### Questions I hope to answer
In China, does a region's economic performance affect its residents' level of support to the authorities?

### Methods
Machine Learning, Automated Text Analysis, Formal Modeling, Agent-based Models.

### Relevant Data
China Family Panel Studies (https://www.icpsr.umich.edu/icpsrweb/ICPSR/studies/36524)

China Multi-Generational Panel Dataset, Liaoning (CMGPD-LN), 1749-1909 (https://www.icpsr.umich.edu/icpsrweb/ICPSR/studies/27063)

China, Europe & Great Divergence (http://doi.org/10.3886/E105383V1)
And many others.

###Summary Statistics
The dataset I use to explore the above question is the China Family Panel Studies (https://www.icpsr.umich.edu/icpsrweb/ICPSR/studies/36524)

Below is the summary statistic of the survey respondents' annual yearly income in 2014, as well as the citizens' attitudes toward government approval. Government approval is measured using an ordinal rank of 1-5, with "1" as most satisfied and "5" as least satisfied.

```{r data, fig.width = 5}
dat <- readstata13::read.dta13(here("data/CFPS.dta"))
summary(dat$p_income)
hist(dat$p_income, main = "Distribution of Resident Income", xlab = "Income (yuan)", ylab = "Frequency")
summary(dat$qn1101)
hist(dat$qn1101, main = "Distribution of Goverment Satisfaction", xlab = "Government Approval Score", ylab = "Frequency")
```

###Experimental GGPlot Data Visualization:
A ggplot2 Graph showing the instinctive relationship between Communist Party membership and income:
```{r ggplot, fig.width = 5}
e <- ggplot(dat, aes(cfps_party, p_income), xlab="Party Membership", ylab="Income")
e + geom_jitter(height = 2, width = 2)
```

<!-- 
Juan,
These all look like great choices from which to select a few interesting variables. You may want to make a separate R script that saves a smaller dataset in a data subfolder and then load it into this script. I'll be interested to see it!
If you have texts (e.g. open survey responses) and want to do your project on word or phrase repetition or frequencies, let's talk about that during office hours. There will be some processing work to do early on.
Best,
Devin 
-->

---


